---
title: ""
output: html_notebook
---

## Loading packages

1.  Load the `tidyverse` in the code chunk below.

```{r}
# SOLUTION:
```

* * *

## Manipulating vectors

The `letters` vector is a vector of all lowercase letters of the alphabet.

2.  Determine the length of the `letters` vector.

```{r}
# SOLUTION:
```


3.  Select the 13th letter of the alphabet.

```{r}
# SOLUTION:
```


4.  Select the 17th through 21st letters of the alphabet.

```{r}
# SOLUTION:
```


* * * 

## Applying functions to vectors

Define the vector `x` to have values 3.2,  9.1,  4.3,  3.6,  8.9 (in that order).


5.  Create the vector `x`.

```{r}
# SOLUTION:
```


6. Run the command `floor(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


7. Run the command `celing(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


8.  Run the command `round(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


9.  Run the command `abs(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


10. Run the command `min(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


11. Run the command `max(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


12. Run that command `which.min(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


13. Run the command `which.max(x)`. Show the output and explain the behavior of the function in your own words.

```{r}
# SOLUTION:
```


* * *

## Manipulating data frames

For the following exercises, load in the built in earthquake data set.

```{r, eval=FALSE}
data(quakes)
```

14.  How would you find information about this data frame? How many rows and 
    columns does it have?
    
```{r}
# SOLUTION:

```



15.  Based purely on the description of the columns (found with `?quakes`), would
    you expect a relationship between the 4th and 5th columns? Why or why not?
    
```{r}
# SOLUTION:

```



16.  Show a command you could use to find the average (mean) magnitude of all 
    earthquakes that occurred below the median depth of all earthquakes.
    
```{r}
# SOLUTION:

```



17.  How does the average magnitude of these "deep" earthquakes compare to the 
    magnitude of "shallow" (above median depth) earthquakes?
    
```{r}
# SOLUTION:

```



18.  Show the command you would use to get the row(s) with the smallest value in 
    the `depth` column.
    
```{r}
# SOLUTION:
```



19. Can you think of an interesting plots you would like to create?  Please 
    experiment around with plotting.
    
```{r}
# SOLUTION:

```
